ms_figures

### 2018-03-20 man/ms_figures.Rmd
include fix figures

themeR <- list(
  geom_errorbar(width=.1, position = pd),
  geom_point(position = pd),
  theme_bw(),
  facet_wrap(~vari, labeller = labeller(vari = variables), scales="free"),
  xlab(''), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    strip.text = element_text(face="bold", size = 14),
    axis.title.y = element_text(face="bold", size = 14),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),
  scale_shape_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = 19, "1_S" = 21, "3_CA-High" = 22, "4_CA-Low" = 15, "2_SJ" = 19)), 
  scale_color_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = 'black', "1_S" = "blue", "3_CA-High" = 'blue', "4_CA-Low" = 'blue', "2_SJ" = 'black')),
  scale_fill_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = 'black', "1_S" = "white", "3_CA-High" = 'white', "4_CA-Low" = 'blue', "2_SJ" = 'black')),
  scale_linetype_manual(labels = item_site, guide = guide_legend(title = NULL),
                        values=c("solid","solid","solid","solid", "solid")),
  scale_size_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = "2", "1_S" = "2", "3_CA-High" = 2.5, "4_CA-Low" = 2.5, "2_SJ" = 2.5)),

@@

**Figure 3.** Response *Q. pyrenaica* forests to drought in terms of resistance, recovery and resilience of greenness (EVI; left-plots) and tree radial growth (BAI; right-plots) for the years 2005 and 2012. For EVI we compared northern populations (black fill circle) with southern ones (blue empty circle). For BAI we compared northern population (San Juan, SJ; black triangle) with southerns populations: Cáñar-High (Ca-H; blue empty squares) and Cáñar-Low (Ca-L; blue fill sauares). Different letters above error bars indicate significant post hoc differences between groups (see material and methods).

>>>>

tl <- guide_legend(title = "Site")

themeR <- list(
  geom_errorbar(width=.1, position = pd),
  geom_point(position = pd),
  theme_bw(),
  facet_wrap(~vari, labeller = labeller(vari = variables), scales="free"),
  xlab(''), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    strip.text = element_text(face="bold", size = 14),
    axis.title.y = element_text(face="bold", size = 14),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),
  scale_shape_manual(labels = item_site, guide = guide_legend(title = "Site"),
    values=c("0_N" = 19, "1_S" = 21, "3_CA-High" = 22, "4_CA-Low" = 15, "2_SJ" = 17)), 
  scale_color_manual(labels = item_site, guide = tl,
    values=c("0_N" = 'black', "1_S" = "blue", "3_CA-High" = 'blue', "4_CA-Low" = 'blue', "2_SJ" = 'black')),
  scale_fill_manual(labels = item_site, guide = tl,
    values=c("0_N" = 'black', "1_S" = "white", "3_CA-High" = 'white', "4_CA-Low" = 'blue', "2_SJ" = 'black')),
  scale_linetype_manual(labels = item_site, guide = tl,
                        values=c("solid","solid","solid","solid", "solid")),
  scale_size_manual(labels = item_site, guide = tl,
    values=c("0_N" = "2", "1_S" = "2", "3_CA-High" = 2.5, "4_CA-Low" = 2.5, "2_SJ" = 2.5)),

@@

**Figure 3.** Response *Q. pyrenaica* forests to drought in terms of resistance, recovery and resilience of greenness (EVI; left-plots) and tree radial growth (BAI; right-plots) for the years 2005 and 2012. For EVI we compared northern populations (*black fill circle*) with southern ones (*blue empty circle*). For BAI we compared northern population (San Juan, SJ; *black triangle*) with southerns populations: Cáñar-High (CA-High; *blue empty squares*) and Cáñar-Low (CA-Low; *blue fill squares*). Different letters above error bars indicate significant *post hoc* differences between groups (see material and methods).
